Workflow for CLM5 paper

### 2018-06-29 Workflow.tex
Updates from ShareLaTeX

Scripts for these analyses should all be found in the public github repo at:
{\color{blue}\small{\url{https://github.com/rosiealice/CLM5_FACE_EXPTS}}}\\

The scripts are specific to usage on the NCAR Cheyenne machine...

@@

\section{Add additional sites}

\section{Add parameters to look at open/closed N cycle}

@@

@@

\section{Add Nitrogen fertilization experiments}

>>>>

Scripts for these analyses should all be found in the public github repo at:\\
{\color{blue}\small{\url{https://github.com/rosiealice/CLM5_FACE_EXPTS}}}\\

The scripts are specific to usage on the NCAR Cheyenne machine...\\

@@

\section{Add parameters to look at open/closed N cycle}
\subsection{Make namelist files witht this matlab script}
{\color{blue}\small{\url{gitpath/matlab/make_namelist_files.m}}}\\
commit 532c208

Files are in here:
{\color{magenta}\small{\url{gitpath/matlab/namelists/**}}}\\
commit c7633e9

\subsection{Make spinup runs for namelist parameters}
{\color{blue}\small{\url{gitpath//case_scripts/make_site_spinup_ensembles}}}\\
commit faa49a9

\subsection{Analyze spinup results for namelist parameters} 
matlab script modified
{\color{blue}\small{\url{gitpath/matlab/CLM5_FACE_senstest_output_mar18.m
}}}\\
e04d71

\subsection{Make transient runs for namelist parameters}

{\color{blue}\small{\url{gitpath//case_scripts/case_scripts/make_site_transient_ELEV_ensembles}}}\\
commit 96fafee

\subsection{Analyze transient runs for namelist parameters}

{\color{blue}\small{\url{gitpath/matlab/CLM5_FACE_senstest_output_ELEV_mar18.m}}}\\
commit fe1a59

@@

\subsection{Modified ranges of flex\_cn\_c parameters}

{\color{blue}\small{\url{gitpath/matlab/FACE_clm5_ens_oaat.m 
}}}\\
commit b3f67e9

Parameter files here:
Output location..\\
{\color{red}\small{\url{gitpath/CLM5_FACE_EXPTS/matlab/FACE_pftfiles/FACE_CLM_params_may1_highleaf_pi13*.nc }}} \\
commit 823385e

\subsection{Set up ensemble runs just for parameter 13}
{\color{blue}\small{\url{gitpath/CLM5_FACE_EXPTS/case_scripts/make_site_spinup_ensembles}} }\\
b3f67e9

\subsection{Set up transient runs just for parameter 13}
{\color{blue}\small{\url{gitpath//case_scripts/case_scripts/make_site_transient_ELEV_ensembles}}}\\
b3f67e9

\subsection{Analyze new runs}

\section{Add Nitrogen fertilization experiments}
\subsection{Made new +5gCm2 file}

\subsection{Make transient NDEP ensembles}
{\color{blue}\small{\url{gitpath/case_scripts/make_site_transient_NDEP_ensembles}}}\\ 
commit 2e395ef

\subsection{Make transient NDEP defaults}
{\color{blue}\small{\url{gitpath/case_scripts/make_site_transient_NDEP_defaults}}}\\ 
commit 2e395ef

\section{Add additional sites}
added Barrow

\section{add temperature experiments}

\section{add reduced form global sensitivity analysis}

 \section{Figures}
 \subsection{Make Will figure}
 \subsection{Make initial LAI figure}
 \subsection{Make 3D figures of parameter space}

@@
